Descriptives and model description

### 2022-12-20 descriptives.qmd
code for binomial model for female/male counts

# Calculate the proportions of children and girls/women
dem_longMissing <- dem_longMissing %>%
  mutate(children = rowSums(select(., female_0_4, female_5_11, female_12_17,
                            male_0_4, male_5_11, male_12_17)),
         adults = rowSums(select(., female_18_59, female_60,
                            male_18_59, male_60)),
         childrenProp = children/total,
         femaleProp = female/total,
         missingAge = case_when(
              missing == "none" ~ "Age not missing",
              missing != "none" ~ "Age missing" 
            )
         )

@@

p.children.gni <- ggplot(data = dem_longMissing_plots,
       aes(x = gni_diff, y = childrenProp, colour = neighbor)) +
  geom_point(shape = 19, aes(size = total, alpha = 0.3)) +  # Add points to the plot
  scale_color_manual(values = c(unhcrPaletteBlue[3], unhcrPaletteBlack[1])) +
  facet_wrap(~ origin_country) + # Group the data by origin_iso3
  scale_size(guide = "none") +
  scale_alpha(guide = "none")

@@

p.children.dist <- ggplot(data = dem_longMissing_plots,
       aes(x = distance, y = childrenProp, colour = neighbor)) +
  geom_point(shape = 19, aes(size = total, alpha = 0.3)) +  # Add points to the plot
  scale_color_manual(values = c(unhcrPaletteBlue[3], unhcrPaletteBlack[1])) +
  facet_wrap(~ origin_country) + # Group the data by origin_iso3
  scale_size(guide = "none") +
  scale_alpha(guide = "none")

p.female.dist <- ggplot(data = dem_longMissing_plots,
       aes(x = distance, y = femaleProp, colour = neighbor)) +
  geom_point(shape = 19, aes(size = total, alpha = 0.3)) +  # Add points to the plot
  scale_color_manual(values = c(unhcrPaletteBlue[3], unhcrPaletteBlack[1])) +
  facet_wrap(~ origin_country) + # Group the data by origin_iso3
  scale_size(guide = "none") +
  scale_alpha(guide = "none")

@@

p.oriregion.missingAge <- p.oriregion.missingAge1  + p.oriregion.missingAge2+ plot_layout(guides = "collect") & theme(legend.position = "bottom", legend.title = element_blank(), legend.text = element_text(size=16))  &  scale_y_continuous(labels = label_number(scale_cut = cut_short_scale()), limits = c(NA,11000000))

>>>>

# Calculate the proportions of children and girls/women
dem_longMissing <- dem_longMissing %>%
  # group_by(asylum_iso3) %>% # begin remove from here to next remove marker once change made in preparedata.R
  #  mutate(distanceAsyMeanW = weighted.mean(distance, w=total, na.rm=T)
  #       ) %>% 
  # ungroup() %>% 
  #  mutate(distance = case_when(
  #          distance == 0 ~ distanceAsyMeanW,
  #          !(distance == 0 ) ~ distance
  #         )
  #       ) %>% 
  # mutate(gniRatio = gni_asylum/gni_origin,
  #        logGniRatio = log(gniRatio),
  #        logDistance = log(distance)
  #       ) %>% 
  #   mutate(children = rowSums(select(., female_0_4, female_5_11, female_12_17,
  #                           male_0_4, male_5_11, male_12_17)),
  #        adults = rowSums(select(., female_18_59, female_60,
  #                           male_18_59, male_60))
  #   ) %>%
  # end remove
  mutate(childrenProp = children/total,
         femaleProp = female/total,
         missingAge = case_when(
              missing == "none" ~ "Age not missing",
              missing != "none" ~ "Age missing" 
            )
         )

@@

## gni
p.children.gni <- ggplot(data = dem_longMissing_plots,
       aes(x = gni_diff, y = childrenProp, colour = neighbor)) +
  geom_point(shape = 19, aes(size = total, alpha = 0.3)) +  # Add points to the plot
  scale_color_manual(values = c(unhcrPaletteBlue[3], unhcrPaletteBlack[1])) +
  facet_wrap(~ origin_country) + # Group the data by origin_iso3 
  scale_size(guide = "none") +
  scale_alpha(guide = "none")

@@

p.children.loggni <- ggplot(data = dem_longMissing_plots,
       aes(x =logGniRatio, y = childrenProp, colour = neighbor)) +
  geom_point(shape = 19, aes(size = total, alpha = 0.3)) +  # Add points to the plot
  scale_color_manual(values = c(unhcrPaletteBlue[3], unhcrPaletteBlack[1])) +
  facet_wrap(~ origin_country) + # Group the data by origin_iso3 
  scale_size(guide = "none") +
  scale_alpha(guide = "none")

p.female.loggni <- ggplot(data = dem_longMissing_plots,
       aes(x = logGniRatio, y = femaleProp, colour = neighbor)) +
  geom_point(shape = 19, aes(size = total, alpha = 0.3)) +  # Add points to the plot
  scale_color_manual(values = c(unhcrPaletteBlue[3], unhcrPaletteBlack[1])) +
  facet_wrap(~ origin_country) + # Group the data by origin_iso3
  scale_size(guide = "none") +
  scale_alpha(guide = "none")

## distance

p.children.dist <- ggplot(data = dem_longMissing_plots,
       aes(x = distance, y = childrenProp, colour = neighbor)) +
  geom_point(shape = 19, aes(size = total, alpha = 0.3)) +  # Add points to the plot
  scale_color_manual(values = c(unhcrPaletteBlue[3], unhcrPaletteBlack[1])) +
  facet_wrap(~ origin_country, scales = "free_x") + # Group the data by origin_iso3
  scale_size(guide = "none") +
  scale_alpha(guide = "none")

p.female.dist <- ggplot(data = dem_longMissing_plots,
       aes(x = distance, y = femaleProp, colour = neighbor)) +
  geom_point(shape = 19, aes(size = total, alpha = 0.3)) +  # Add points to the plot
  scale_color_manual(values = c(unhcrPaletteBlue[3], unhcrPaletteBlack[1])) +
  facet_wrap(~ origin_country, scales = "free_x") + # Group the data by origin_iso3
  scale_size(guide = "none") +
  scale_alpha(guide = "none")

p.children.logdist <- ggplot(data = dem_longMissing_plots,
       aes(x = logDistance, y = childrenProp, colour = neighbor)) +
  geom_point(shape = 19, aes(size = total, alpha = 0.3)) +  # Add points to the plot
  scale_color_manual(values = c(unhcrPaletteBlue[3], unhcrPaletteBlack[1])) +
  facet_wrap(~ origin_country, scales = "free_x") + # Group the data by origin_iso3
  scale_size(guide = "none") +
  scale_alpha(guide = "none")

p.female.logdist <- ggplot(data = dem_longMissing_plots,
       aes(x = logDistance, y = femaleProp, colour = neighbor)) +
  geom_point(shape = 19, aes(size = total, alpha = 0.3)) +  # Add points to the plot
  scale_color_manual(values = c(unhcrPaletteBlue[3], unhcrPaletteBlack[1])) +
  facet_wrap(~ origin_country, scales = "free_x") + # Group the data by origin_iso3
  scale_size(guide = "none") +
  scale_alpha(guide = "none")

@@

p.oriregion.missingAge <- p.oriregion.missingAge1  + p.oriregion.missingAge2+ plot_layout(guides = "collect") & theme(legend.position = "bottom", legend.title = element_blank(), legend.text = element_text(size=16))  &  scale_y_continuous(labels = label_number(scale_cut = cut_short_scale()), limits = c(NA,11000000)) & theme(title = )
